\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-17 manuscript.Rmd
updates
Bye Bye Hard Coding!

Timeline of data collection, ethical approval mode of data collection how consent was recorded.

@@

```{r factordetails, include=FALSE}
#Preparing the EFA table
factor.des = matrix(, nrow = 27, ncol = 6)
as.table(factor.des)
rownames(factor.des) <- c("item16", "item36",  "item17",   
                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
                          "item27", "item3",  "item40","item30","item41",
                          "item33", "item32", "item35","item37", "item38",
                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")

colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")

factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))

factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))

factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))

factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))

factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))

factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")

@@

apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
```

>>>>

Timeline of data collection, mode of data collection.

@@

```{r factordetails, include=FALSE}
#Preparing the EFA table
fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(2)
  #supress loadings
  loadings[abs(loadings) < abs(cut)] <- ""
  #get additional info
  add_info <- cbind(x$communality, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(across(where(is.numeric), round, 3))
}
efa.tab <- fa_table(fa.5F.3,.3)

variance <- fa.5F.3$Vaccounted %>% 
  as.data.frame()%>% 
  round(2)
library(data.table)
efa.table <- rbind(setDT(efa.tab), setDT(variance[2,]), fill=TRUE)
efa.table[26,1] <- "% of variance"

@@

apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
```
